Sample-efficient Reinforcement Learning with Implicitly Quantized Representations

### 2024-02-01 paper/main.tex
use humanoid for fig 1

  \node[mynode,above of=e0] (i0) {\includegraphics[width=4.7em]{figs/bg}};
  \node[mynode,above of=e1] (i1) {\includegraphics[width=4.7em]{figs/bg}};
  \node[mynode,above of=e2] (i2) {\includegraphics[width=4.7em]{figs/bg}};

>>>>

  \node[mynode,above of=e0] (i0) {\includegraphics[width=4.7em]{figs/humanoid-1}};
  \node[mynode,above of=e1] (i1) {\includegraphics[width=4.7em]{figs/humanoid-2}};
  \node[mynode,above of=e2] (i2) {\includegraphics[width=4.7em]{figs/humanoid-3}};
